Automated Software Engineering Final Paper (Working Title)

### 2015-12-12 paper/paper.tex
Added Bird paper to related work

>>>>

Bird et al \cite{Bird} examined whether development that is largely distributed produces more failures than development that is mainly collocated. The belief at the time was that distributed development was prone to more failures than collocated development. They found a negligible difference in both code metrics and failures between the two methods of development. The authors examined how the developers working on Windows Vista managed to work well together among teams located in different countries based on the relationships between the development sites, cultural barriers, communication, consistent use of tools, end to end ownership, common schedules, and organizational integration. They recommended that companies wishing to distribute development across sites located far apart to employ similar strategies to overcome some of the difficulties associated with such an endeavor.
